On the discretization of Laplace's equation with Neumann boundary conditions on polygonal domains

### 2020-06-10 paper_lap/JCP_response2/06num.tex
update

\begin{rem}
Though $2^{-200}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by translating the corners to the origin when 
computing interactions of nearby points.
\end{rem} 
\begin{rem}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, resulting values of the density will not be 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are at least $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-200}$. 
\end{rem}

The potential at target locations which are sufficiently far from the boundary (i.e. at least one panel length away from 
every panel) is the inner product of the 
density with a smooth function and hence can be computed accurately without re-solving (see~\cref{rem:far-field-accuracy}). For a target 
location $\boldsymbol{y}$, we compute the potential via the formula,
\begin{equation}
\label{eq:farfieldpot}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In~\cref{fig:scatteringtest}, we compute the error in the solution at target
locations for a scattering problem whose right hand side is given by a collection of three interior charges
\begin{equation}
\label{eq:scatboundarydata}
f(\bx) = -\nabla  \left(\sum_{j=1}^{3} \log |\bx - \bx_{j}|  \right)  \cdot \bnu(\bx)\, ,  
\end{equation}
where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:scatteringtest}. Note that the density $\sigma$ plotted
as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
presented in~\cref{sec:disc_dir} wouldn't have sufficed. However, the potential in the volume is accurate to 14 digits at
target locations away from the boundary. 
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{paper-figs/weaktest}
\caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arc-length}.
\label{fig:scatteringtest}
\end{center}
\end{figure}

Another example of a ``weak quantity'' is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint discretization
are given by
\begin{equation}
P = \begin{bmatrix}
-0.823641009939200 & -0.139714174784448 \\
 -0.139714174784448 &  -1.1421444446470226
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
2.3 \times 10^{-15} & 7.9 \times 10^{-16} \\
1.3 \times. 10^{-14} & 2.7 \times 10^{-15}
\end{bmatrix}
\end{equation}

@@

\subsection{Performance}
In this section, we demonstrate the performance of the solver by solving a scattering problem in the
exterior of a ``broken wheel'' region. The boundary data is given by
\begin{equation}
f(x) = \nabla  \sum_{j=1}^{57} c_{j} \log| \bx - \bx_{j}| \cdot \bnu(\bx) \, , 
\end{equation}
where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exterior of the bounding disc containing the domain. The strengths $c_{j}$ are chosen such that they average to $0$. The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations to converge to a residue of $10^{-15}$. The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$. The solution was computed in $15$ secs, and plotted at a $500\times 500$ grid of targets in $6.5$ secs. All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors. In~\cref{fig:magnetron}, we plot the scattered field, the boundary data, and the computed density.

>>>>

\begin{remark1}
Though $2^{-200}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by translating the corners to the origin when 
computing interactions of nearby points.
\end{remark1} 
\begin{remark1}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, resulting values of the density will not be 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are at least $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-200}$. 
\end{remark1}

The potential at target locations which are sufficiently far from the boundary (i.e. at least one panel length away from 
every panel) is the inner product of the 
density with a smooth function and hence can be computed accurately without re-solving (see~\cref{rem:far-field-accuracy}). For a target 
location $\boldsymbol{y}$, we compute the potential via the formula,
\begin{equation}
\label{eq:farfieldpot}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}.
\end{equation}
In~\cref{fig:scatteringtest}, we compute the error in the solution at target
locations for a scattering problem whose {\color{olive}boundary condition} is given by a collection of three interior charges
\begin{equation}
\label{eq:scatboundarydata}
f(\bx) = -\nabla  \left(\sum_{j=1}^{3} \log |\bx - \bx_{j}|  \right)  \cdot \bnu(\bx)\, ,  
\end{equation}
where the locations $\bx_{j}$ are denoted by square dots in~\cref{fig:scatteringtest}. Note that the density $\sigma$ plotted
as a function of arclength goes to infinity at the corner vertices, indicating that the native Dirichlet discretization 
presented in~\cref{sec:disc_dir} wouldn't have sufficed. However, the potential in the volume is accurate to 14 digits at
target locations away from the boundary. 
\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{paper-figs/weaktest}
\caption{Left panel: Solution to Neumann problem with data given by~\cref{eq:scatboundarydata}, center panel: error in computing the potential in the formula using the underlying smooth quadrature~\cref{eq:farfieldpot}, and on the right the density $\sigma$ as a function of arclength}.
\label{fig:scatteringtest}
\end{center}
\end{figure}

Another example of a ``weak quantity'' is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}.
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint discretization
are given by
\begin{equation}
P = \begin{bmatrix}
-0.823641009939200 & -0.139714174784448 \\
 -0.139714174784448 &  -1.1421444446470226
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
2.3 \times 10^{-15} & 7.9 \times 10^{-16} \\
1.3 \times. 10^{-14} & 2.7 \times 10^{-15}
\end{bmatrix}.
\end{equation}

@@

\subsection{Performance}
In this section, we demonstrate the performance of the solver by solving a scattering problem in the
exterior of a ``broken wheel'' region. The boundary data is given by
\begin{equation}
f(x) = \nabla  \sum_{j=1}^{57} c_{j} \log| \bx - \bx_{j}| \cdot \bnu(\bx) \, , 
\end{equation}
where there is one $\bx_{j}$ located in each of the spokes, one of the $\bx_{j}$ is in the central disc, and the remaining $50$ $\bx_{j}$ are chosen randomly in the exterior of the bounding disc containing the domain. The strengths $c_{j}$ are chosen such that they average to $0$. The domain contains $108$ corners, was discretized using $22240$ nodes and required $105$ iterations {\color{olive}of GMRES} to converge to a residue of $10^{-15}$. The matrix at each iteration was applied using an FMM whose tolerance was also set to $10^{-15}$. The solution was computed in $15$ secs, and plotted at a $500\times 500$ grid of targets in $6.5$ secs. All of the results have been computed on a single core on a Macintosh machine with Intel core i5 2.3GHz processors. In~\cref{fig:magnetron}, we plot the scattered field, the boundary data, and the computed density.

### 2020-06-10 paper_lap/JCP_response2/Significance.tex
update

\begin{document}
 \title{Significance and novelty of this paper}
 \maketitle
The solution to boundary integral equations corresponding to Laplace's equations
with polygonal domains
develop singularities near corners; this poses a challenge for designing
efficient numerical methods for their solution. 
If the boundary data on each edge of the polygon is smooth, then the solution
to the corresponding boundary equation has an expansion terms of certain analytically
available singular powers. 
Using the known behavior of he solution to the integral equation, efficient
discretizations have been constructed for the Dirichlet problem.
However, these methods do not directly extend to the solution of the Neumann problem
since the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ 
for $\mu \in (-1/2,1/2)$ depending on the angle at the corner, while that of solutions
to the Dirichlet problem is $O(C + t^{\mu})$ for $\mu>1/2$.

In this paper, we present a universal discretization for the solution of the Neumann problem
on polygonal domains based on an adjoint Dirichlet discretization.
We show that the solution obtained in this manner is accurate in a ``weak-sense'', i.e. 
inner-products of the solution with smooth functions can be computed accurately. 
Further, we show that the solution is also accurate point wise away from the corners. 
We also present an algorithm to obtain accurate solutions in the vicinity of the corner
by solving a series of local sub-problems in the vicinity of the corner. 
This enables accurate evaluation of the corresponding potential at target locations arbitrarily
close to the corner. We present the effectiveness of our method, both in terms of accuracy
and speed through several numerical examples.
\end{document}

>>>>

\begin{document}
 \title{Significance and novelty of this paper}
 \maketitle
The solutions to boundary integral equations corresponding to Laplace's equations
with polygonal domains
develop singularities near corners; this poses a challenge for designing
efficient numerical methods for their solution. 
If the boundary data on each edge of the polygon is smooth, then the solution
to the corresponding boundary integral equation has an expansion in terms of certain analytically
available singular powers. 
Using the known behavior of the solution to the integral equation, efficient
discretizations have been constructed for the Dirichlet problem.
However, these methods do not directly extend to the solution of the Neumann problem
since the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ 
for $\mu \in (-1/2,1/2)$ depending on the angle at the corner, while that of solutions
to the Dirichlet problem is $O(C + t^{\mu})$ for $\mu>1/2$.

In this paper, we present a universal discretization for the solution of the Neumann problem
on polygonal domains based on an adjoint Dirichlet discretization.
We show that the solution obtained in this manner is accurate in a ``weak-sense'', i.e. 
inner-products of the solution with smooth functions can be computed accurately. 
Further, we show that the solution is also accurate pointwise away from the corners. 
We also present an algorithm to obtain accurate solutions in the vicinity of the corner
by solving a series of local subproblems in the vicinity of the corner. 
This enables accurate evaluation of the corresponding potential at target locations arbitrarily
close to a corner. We present the effectiveness of our method, both in terms of accuracy
and speed through several numerical examples.
\end{document}

### 2020-06-10 paper_lap/JCP_response2/manuscript.tex
update

\begin{abstract}
In the present paper we describe a class of algorithms for the solution of Laplace's equation on polygonal domains with Neumann boundary conditions. It is well known that in such cases the solutions have singularities near the corners which poses a challenge for many existing methods. 
If the boundary data is smooth on each edge of the polygon, then in the vicinity of each corner the solution to the corresponding boundary integral equation has an expansion in terms of certain (analytically available) singular powers. Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem. 
However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for $\mu \in (-1/2,0)$ depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations. Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.  Furthermore we present a procedure to obtain accurate solutions arbitrarily close to the corner, by solving a sequence of small local subproblems in the vicinity of that corner. The results are illustrated with several numerical examples.
\end{abstract}

\begin{highlights}
\item Efficient discretization to boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions on polygonal domains based on an adjoint Dirichlet discretization resulting
in weak solutions to the integral equation. 
\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner.
\item Rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
\end{highlights}

@@

\appendix
\section{Approximation of data on corner panels for re-solve}
Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel. In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$

%Let $\Gamma_*$ be any other straight line segment contained entirely within $\Gamma \setminus B_{2r}(\bx).$ Then

\begin{theorem}
Let $\Gamma$ be the boundary of a polygon and $\bx$ be a vertex. Let $r>0$ be a real number such that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r,$ where $B_R(\bx)$ denotes a ball of radius $R$ centered at $\bx.$ Let $L$ denote the length of $\Gamma$ and $\gamma: [-L/2,L/2]\to \Gamma$ be an arclength counterclockwise parameterization of $\Gamma$ such that $\gamma(0) = \bx.$ Finally, for any $f \in L^2(\Gamma),$ let $H:[0,r] \to \mathbb{R}$ be the function defined by
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s.
\end{align}
Then $H$ is analytic in a neighborhood of $0$ with Taylor series coefficients $\{ a_n\}$ satisfying
\begin{align}
|a_n| \le \frac{\sqrt{L}}{2^nr^{n+1}} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{theorem}
\begin{proof}
Without loss of generality we can assume that $\Gamma$ is shifted, oriented and parameterized so that $\bx = \gamma(0)= 0$ and the leg of the wedge corresponding to positive $t$ is oriented along the positive $x$ axis. Then
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s = \int_{\Gamma\backslash B_{2r}(\bx)} \frac{y(s)}{(t-x(s))^2+y(s)^2}f(s)\,{\rm d}s.
\end{align}
Since $\|\gamma(s)-\gamma(t)\| >2r$ it follows that
\begin{align}
H(t) =\int _{\Gamma\backslash B_{2r}(\bx)}\sum {t^n i}\left(\frac{1}{(x(s)+i y(s))^{n+1}}-\frac{1}{(x(s)-i y(s))^{n+1}} \right) f(s)\,{\rm d}s.
\end{align}
In particular, $H$ has a Taylor series about $t=0,$
\begin{align}
\sum_{n=0}^\infty c_n \left(\frac{t}{2r}\right)^n
\end{align}
where
\begin{align}
|c_n| \le  \frac{\sqrt{L}}{r} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{proof}

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
{\color{blue}
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = \mathbb{L}^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
$S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.

Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential. Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution.   Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$. Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
\begin{equation}
e = \max_{i=1,2\ldots M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
\end{equation}

@@

\Cref{lem:b2} shows that the error in evaluating the inner product of the computed density $\usigma$ with a polynomial on
$\Gamma_{\ell}$ is the same as the error in evaluating the inner product of a computed density for a Dirichlet problem $\usigma_{D,i}$ with boundary data $g$. 
The Dirichlet boundary data $f_{i}$ (\cref{eq:deff}) corresponding to the density $\sigma_{D,i}$ is an analytic function on each of the edges of the polygon. 
The discretization of $A$ of~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization. Since $g$ is also a smooth function, given a tolerance $\varepsilon$, there exists a sufficiently fine discretization of the boundary such that
\begin{equation}
\left| \left< g, \sigma_{D,i} \right>_{X} - \left< S[g], \usigma_{D,i} \right>_{\uX} \right| < \varepsilon \, . \label{eq:dest}
\end{equation}
In practice, a discretization with macroscopic panels at the corner, panels not at a corner vertex separated from the corner by their panel length, and which resolves $g$ to precision $\varepsilon$ is often sufficient to guarantee~\cref{eq:dest}. 
\begin{rem}
The size of the panel at the corner needs to be chosen based on the angle formed at the corner---smaller panels for angles closer to $0$ or $2\pi$, in order to resolve the corresponding close to touching interactions.
\end{rem}
}

>>>>

\begin{abstract}
In the present paper we describe a class of algorithms for the solution of Laplace's equation on polygonal domains with Neumann boundary conditions. It is well known that in such cases the solutions have singularities near the corners which poses a challenge for many existing methods. 
If the boundary data is smooth on each edge of the polygon, then in the vicinity of each corner the solution to the corresponding boundary integral equation has an expansion in terms of certain (analytically available) singular powers. Using the known behavior of the solution, universal discretizations have been constructed for the solution of the Dirichlet problem. 
However, the leading order behavior of solutions to the Neumann problem is $O(t^{\mu})$ for {\color{olive}$\mu \in (-1/2,1/2)$} depending on the angle at the corner (compared to $O(C+t^{\mu})$ with $\mu>1/2$ for the Dirichlet problem); this presents a significant challenge in the design of universal discretizations. Our approach is based on using the discretization for the Dirichlet problem in order to compute a solution in the ``weak sense'' by solving an adjoint linear system; namely, it can be used to compute inner products with smooth functions accurately, but it cannot be interpolated.  Furthermore we present a procedure to obtain accurate solutions arbitrarily close to the corner, by solving a sequence of small local subproblems in the vicinity of that corner. The results are illustrated with several numerical examples.
\end{abstract}

\begin{highlights}
{\color{olive}
\item Efficient discretization of boundary integral equations corresponding to Laplace's equation with Neumann boundary conditions on polygonal domains based on an adjoint Dirichlet discretization resulting
in weak solutions to the integral equation. 
\item A local re-solve algorithm for obtaining pointwise accurate solutions of the integral equation arbitrarily close to the corner, and rapid evaluation of solution at target locations in the volume arbitrarily close to the corner.
\item Accurate solution of Laplace's equation arbitrarily close to corners at which solutions may have singularities.}
\end{highlights}

@@

\appendix
\section{Approximation of data on corner panels for re-solve}
Here we give explicit bounds for the rate of convergence of the contribution of the rest of the boundary to a corner panel.{\color{red} In particular, given a polygonal domain with boundary $\Gamma,$ let $\bx$ denote a vertex of $\Gamma$ and $C = \Gamma \cap B_r(\bx),$ where $B_r(\bx)$ is the ball of radius of $r$ centered at $\bx.$ We choose $r$ so that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r.$ }

\begin{theorem}
Let $\Gamma$ be the boundary of a polygon and $\bx$ be a vertex. Let $r>0$ be a real number such that $\Gamma \cap B_{2r}(\bx)$ corresponds to a wedge with internal angle $\pi \alpha$ and side lengths $2r,$ where $B_R(\bx)$ denotes a ball of radius $R$ centered at $\bx.$ Let $L$ denote the length of\, $\Gamma$ and $\gamma: [-L/2,L/2]\to \Gamma$ be an arclength counterclockwise parameterization of\, $\Gamma$ such that $\gamma(0) = \bx.$ Finally, for any $f \in L^2(\Gamma),$ let $H:[0,r] \to \mathbb{R}$ be the function defined by
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(\gamma(s))\,{\rm d}s.
\end{align}
Then $H$ is analytic in a neighborhood of $0$ with Taylor series coefficients $\{ a_n\}$ satisfying
\begin{align}
|a_n| \le \frac{\sqrt{L}}{2^nr^{n+1}} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{theorem}
\begin{proof}
Without loss of generality we can assume that $\Gamma$ is shifted, oriented and parameterized so that $\bx = \gamma(0)= 0$ and the leg of the wedge corresponding to positive $t$ is oriented along the positive $x$ axis. Then
\begin{align}
H(t) = \int_{\Gamma\backslash B_{2r}(\bx)} K(\gamma(t),\gamma(s)) f(s)\,{\rm d}s = \int_{\Gamma\backslash B_{2r}(\bx)} \frac{y(s)}{(t-x(s))^2+y(s)^2}f(s)\,{\rm d}s.
\end{align}
Since $\|\gamma(s)-\gamma(t)\| >2r$ it follows that
\begin{align}
H(t) =\int _{\Gamma\backslash B_{2r}(\bx)}\sum {t^n i}\left(\frac{1}{(x(s)+i y(s))^{n+1}}-\frac{1}{(x(s)-i y(s))^{n+1}} \right) f(s)\,{\rm d}s.
\end{align}
In particular, $H$ has a Taylor series about $t=0,$
\begin{align}
\sum_{n=0}^\infty c_n \left(\frac{t}{2r}\right)^n
\end{align}
where
\begin{align}
|c_n| \le  \frac{\sqrt{L}}{r} \|f\|_{L_2(\Gamma \backslash B_{2r}(\bx))}.
\end{align}
\end{proof}

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
{\color{blue}
In this section, we demonstrate that for a panel which is sufficiently far from the corner, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [0,L]\to \mathbb{R}^2$ denote an arc-length parameterization of the boundary. Suppose that the boundary is discretized using the procedure discussed in~\cref{sec:resolve}. Recall that the discretizaton nodes are denoted by $x_{1},x_{2}\ldots x_{N}$, the corresponding weights are given by $w_{1}, \ldots w_{N}$, $X = \mathbb{L}^2({\Gamma})$, $\underline{X} = \mathbb{R}^{N}$, $\left< \cdot, \cdot \right>_{Y}$
denote the standard inner products on the Hilbert spaces $Y=X,\underline{X}$, and
$S:X \to \uX$ denote the operator which samples a function on the boundary at the discretization nodes scaled by the square root of the weights, i.e. 
\begin{equation}
S[f] = (f(x_{1})\sqrt{w_{1}},f(x_{2})\sqrt{w_{2}},\ldots, f(x_{N}) \sqrt{w_N} )^{T} = \underline{f} \, .
\end{equation}
Let $P:\underline{X} \to X$ denote the operator mapping the discretized samples to it's piecewise interpolant on the boundary.
Let $\Gamma_{\ell} = \gamma([s_{1},s_{2}])$ denote a panel that does not contain a corner vertex and is discretized with $M$ nodes  $x_{i},x_{i+1},\ldots x_{i+M-1}$.

Let $A$ denote operator corresponding to the interior Dirichlet problem where the solution is represented as a double layer potential. Let $\underline{A}$ denote the $N\times N$ matrix corresponding to the discretization of $A$. Let $g$ denote the
right-hand side for the Neumann problem, and let $\sigma$ denote the corresponding solution.   Let $\underline{\sigma}$ denote the solution of the linear system $\uA^{T} \usigma = S[g]$. Let $h_{i}$, $i=1,2,\ldots M$, denote the scaled Legendre polynomials to the panel $\Gamma_{\ell}$.
The main result of this appendix is to show that under suitable assumptions, that the computed density can be accurately interpolated on $\Gamma_{\ell}$, i.e.  
\begin{equation}
e = \max_{i=1,2\ldots, M} |\left< \sigma, h_{i} \right>_{X} -  \left< \usigma, S[h_{i}] \right>_{\uX}| < \varepsilon  
\end{equation}

@@

\Cref{lem:b2} shows that the error in evaluating the inner product of the computed density $\usigma$ with a polynomial on
$\Gamma_{\ell}$ is the same as the error in evaluating the inner product of a computed density for a Dirichlet problem $\usigma_{D,i}$ with boundary data $g$. 
The Dirichlet boundary data $f_{i}$ (\cref{eq:deff}) corresponding to the density $\sigma_{D,i}$ is an analytic function on each of the edges of the polygon. 
The discretization of $A$ in~\cite{hoskins2019numerical} is precisely designed to compute $\sigma_{D,i}$ accurately to any desired tolerance, under sufficient refinement of the discretization. Since $g$ is also a smooth function, given a tolerance $\varepsilon$, there exists a sufficiently fine discretization of the boundary such that
\begin{equation}
\left| \left< g, \sigma_{D,i} \right>_{X} - \left< S[g], \usigma_{D,i} \right>_{\uX} \right| < \varepsilon \, . \label{eq:dest}
\end{equation}
In practice, a discretization with macroscopic panels at the corner, panels not at a corner vertex separated from the corner by their panel length, and which resolves $g$ to precision $\varepsilon$ is often sufficient to guarantee~\cref{eq:dest}. 
\begin{rem}
The size of the panel at the corner needs to be chosen based on the angle formed at the corner---smaller panels for angles closer to $0$ or $2\pi$, in order to resolve the corresponding close to touching interactions.
\end{rem}
}
